---
title: "Quarto Final Project"
author: "Kinesso Kombate"
format: html
execute:
  echo: true
---
```{r}
#| label: loading
#| message: false
library(gtsummary)
library(tidyverse)
library(here)
library(broom)
library(ggplot2)
```

# DATA

The dataset `childcare_costs` comes from the National Database of Childcare Prices (NDCP). It is the most comprehensive federal source of childcare prices at the county level. The database offers childcare price data by childcare provider type, age of children, and county characteristics. The data available is from 2008 to 2018.

```{r}
#| label: load-data
childcare_costs <- read_csv(here::here("childcare_costs.csv"))
table1 <- tbl_summary(
	childcare_costs,
	by = study_year,
	include = c(unr_16,funr_16,unr_20to64,
							funr_20to64,flfpr_20to64,flfpr_20to64_6to17,pr_f,one_race_b),
	label= list(unr_16 ~ "Unemployment rate of the population ages 16 y/o <",
							funr_16 ~ "Unemployment rate of the female population ages 16 y/o <",
							unr_20to64 ~ "Unemployment rate of the population ages 20 - 64 y/o",
							funr_20to64 ~ "Unemployment rate of the female population ages 20 - 64 y/o",
							flfpr_20to64 ~ "Labor force participation rate of the female population ages 20 - 64 y/o",
							flfpr_20to64_6to17 ~ "Labor force participation rate of the female population ages 20 - 64 y/o who have children between 6 - 17 y/o",
							pr_f ~ "Poverty rate for families",
							one_race_b ~ "Percent of population that identifies as being one race and being only Black or African American"),
	missing_text = "Missing"
)

table1
```

# Table

(@tbl-uvreg) shows the univariate association between each labor market predictor and median household income.

```{r}
#| label: tbl-uvreg
#| tbl-cap: "Univariate regressions predicting median household income (2018 dollars)"

uv_regression <- tbl_uvregression(
	childcare_costs,
	y = mhi_2018,
	include = c(
		unr_16,funr_16,unr_20to64,
		funr_20to64,flfpr_20to64,flfpr_20to64_6to17,pr_f,one_race_b),
	method = lm)|>
  bold_labels()
uv_regression

linear_model <- lm(mhi_2018 ~ me_2018 + fme_2018 + mme_2018, data = childcare_costs)

tidy(linear_model)
```

```{r}
scatterplot <- ggplot(childcare_costs,
			 aes(x = mme_2018, y = fme_2018)) +
	geom_point(aes(colour = mhi_2018)) +
	labs(
		x = "Median Earnings for the Male Population 16 y/o < (2018 $)",
		y = "Median Earnings for the Female Population 16 y/o < (2018 $)",
		color = "Median Household Income (2018 $)",
		title = "Median Incomes in 2018"
	) +
	theme_classic()
scatterplot
```
